\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-28 paper/intersection.tex
Enlarged intersection.tex

\section{Lawful Intersection Warrants}\label{sec-intersection}
In this section, we present an improved implementation of the lawful
set-intersection protocol of~\cite{sff-foci2014}. 
{\bf Create Subsections 3.1 and 3.2.  Add something about why this protocol
satisfies the openness principle.}

@@

The agencies can then directly compare Pohlig-Hellman ciphertexts to each 
other to determine which appear in the intersection of all three sets of data. 
If the intersection is much larger than expected, any one of the agencies can 
delete its Pohlig-Hellman decryption key to prevent any user data from being 
revealed until a more narrowly scoped warrant can be agreed upon. Otherwise, 
the agencies finish the protocol by using their Pohlig-Hellman decryption keys 
to reveal only the ciphertexts in the intersection of all three sets.

\subsection{Improved Implementation of Lawful Intersection}

@@

{\bf Add something about the argument that SFF made about their protocol's
being fast enough.}

We have produced an improved implementation
that takes advantage of parallel processing and more advanced computational 
hardware, thus showing that lawful set-intersection can be performed 
much more quickly than originally descrbied in~\cite{sff-foci2014}.

>>>>

\section{Lawful Intersection Warrants}\label{sec-intersection}
In this section, we present an improved implementation of the lawful
set-intersection protocol of~\cite{sff-foci2014}. 
\subsection{Intersections and Privacy}

As described in Section~\ref{sec-intro} and in~\cite{sff-foci2014}, the FBI used
set intersection to search for phone numbers that appeared in three sets of
cell-tower dumps. This procedure did not follow the the openness principle.
The FBI did not distinguish between targeted and untargeted users when
collecting the data. It only arrested the user in the intersection of the sets
it collected, as far as we know, but as there was no established accountability
procedure, we do not know whether the FBI retained the phone numbers of
untargeted users collected during the search, whether it subjected any of those
other phone numbers to additional investigation, whether it shared the data sets
of 150,000 total users with other government agencies, \it{etc}.

Segal \it{et al.}~\cite{sff-foci2014} presented a private set intersection
protocol to address these specific concerns. We present a summary of that protocol
in Section~\ref{sec-isectproto}. This protocol reveals \emph{only} the identities
of users in the intersection of the sets under consideration, leaving the other,
untargeted users' identities hidden by encryption. To provide accountability and
oversight, the protocol requires multiple government agencies to participate. This
provides a division of authority. No one agency can uncover users' identities
without other agencies being able to collect records about how often intersection
warrants are used and set restrictions on how many users the agencies can identify
under a single warrant.

The lawful contact chaining protocol we present in Section~\ref{sec-chaining} will
produce large, encrypted sets of user identities. These sets can then be used as
inputs into the lawful set intersection protocol, to reveal the small, targeted
group of identities that appear in multiple sets (whether those sets come from cell
tower dumps as in the High Country Bandits case, contact chaining, or some other
legally obtained source of information).

\subsection{Lawful Intersection Protocol}\label{sec-isectproto}

@@

The agencies can then directly compare Pohlig-Hellman ciphertexts to each 
other to determine which appear in the intersection of all sets of data. 
If the intersection is much larger than expected, any one of the agencies can 
delete its Pohlig-Hellman decryption key to prevent any user data from being 
revealed until a more narrowly scoped warrant can be agreed upon. Otherwise, 
the agencies finish the protocol by using their Pohlig-Hellman decryption keys 
to reveal only the ciphertexts in the intersection of all sets.

\subsection{Improved Implementation of Lawful Intersection}\label{sec-isectimpl}

@@

In an experiment with 150,000 users - the same number of users as the FBI
examined in the High Country Bandits case - that implementation took
approximately two hours to run to completeion. As the authors argued an FBI
investigation is likely to take days to lead to an arrest, even without the
use of this privacy-preserving technology. Therefore, a two-hour running time
may not be a major obstacle in this context.

But because we offer a new use of the lawful intersection protocol, we
also offer a speedier implementation of it. Our improved implementation
takes advantage of parallel processing and more advanced computational 
hardware, thus showing that lawful set-intersection can be performed 
much more quickly than originally described in~\cite{sff-foci2014}.
